### 2019-02-27 papers/journal/encoding.tex
Updated Fusion encoding for SMT
Fusion 2 encoding
Update on BMC

\subsubsection{Well-fused constraints}
Constraint~\eqref{eq:fuse1} encodes that each edge must fuse with
its destination node.
%
Constraint~\eqref{eq:fuse2} encodes that each edge should not
be able to potentially fuse with any node other than its destination node.
\begin{align}
  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies \bigvee_{m,m^{\prime}} (b_{i,j,q,m} \land a_{j,m^{\prime}} \land p_{m,m^{\prime}})
  \tag{V7}\label{eq:fuse1}  \\
\bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies \neg \bigvee_{j \neq j^{\prime}, m^{\prime\prime}} ( a_{j^{\prime},m^{\prime\prime}} \land p_{m,m^{\prime\prime}})
  \tag{V8}\label{eq:fuse2}  
\end{align}

@@

The BMC encoding differs with the presented SMT encoding slightly in the way variables are represented and how we encode reachability.  
%
Variables are not Boolean indexed with multiple dimensions but arrays of bitvectors of size $\mu$. 
%
%We initialize the system with a fixed number of node size (N) and distinct molecular types (M). 
%%
%We use a two-dimensional array variable \textit{Graph}[N][N] to represent the transport graph. The graph variable is set to x, Graph[i][j] = x, if there are exactly x edges between node i and j. 
%\begin{align*}
%graph [i] [j] = x.
%\end{align*}
%
For examplei, the edges are represented as a bitvectors of size M with each bit corresponding to the presence or the absence of the molecule. 
%
The index of the bitvector implicitly determines the corresponding molecule we are referring to.
%
Bit vector $bv\_e[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
%

@@

We encode stability using NOracle and if there is an $m$-edge between node $i$ and $j$, there has to be a $m$-path from $j$ to $i$ of length maximum w.
%
%We have used bv $\unrhd$ m to extract the $m^{th}$ bit of the bitvector bv. 
\begin{align}
 \bigwedge\limits_{i,j,m} (\bigvee_{q} bv\_e[i][j][q] \limplies NOracle(m, j, i, w)
  \tag{S2}\label{eq:reachbmc2}
\end{align}

%\begin{align}
% \bigwedge\limits_{i,j,m} (\bigvee_{q} (bv\_e[i][j][q] \unrhd m) > 0) \limplies NOracle(m, j, i, w)
 % \tag{S2}\label{eq:reachbmc2}
%\end{align}

>>>>

\subsubsection{Well-fused constraints}
Constraint~\eqref{eq:fuse1} encodes that each edge must fuse with
its destination node.
%
Constraint~\eqref{eq:fuse2} encodes that each edge should not
be able to potentially fuse with any node other than its destination node.
\begin{align}
  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies 
\bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land
\Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land
  \notag\\	
	\Lor\limits_{l=1}^4 a_{j,m_l} \land p_{\{m_1,m_2,m_3,m_4\}})
  \tag{V7}\label{eq:fuse1}  
\end{align}

\begin{align}
	\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies
\mspace{250mu}
  \notag\\
	\neg
\bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land .. \land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
  \tag{V8}\label{eq:fuse2}  
\end{align}

@@

The BMC encoding differs with the presented SMT encoding slightly in the way variables are represented and how we encode reachability.  
%
Variables are not Boolean indexed with multiple dimensions but arrays of bitvectors of size $\mu$. 
%
%We initialize the system with a fixed number of node size (N) and distinct molecular types (M). 
%%
%We use a two-dimensional array variable \textit{Graph}[N][N] to represent the transport graph. The graph variable is set to x, Graph[i][j] = x, if there are exactly x edges between node i and j. 
%\begin{align*}
%graph [i] [j] = x.
%\end{align*}
%
For example, the edges are represented as a bitvectors of size M with each bit corresponding to the presence or the absence of the molecule. 
%
The index of the bitvector implicitly determines the corresponding molecule we are referring to.
%
Bit vector $bv\_e[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
%

@@

We encode stability using NOracle and if there is an $m$-edge between node $i$ and $j$, there has to be a $m$-path from $j$ to $i$ of length maximum w.
%
We have used bv $\unrhd$ m to extract the $m^{th}$ bit of the bitvector bv.

\begin{align}
 \bigwedge\limits_{i,j,m} (\bigvee_{q} (bv\_e[i][j][q] \unrhd m) == 1) \limplies NOracle(m, j, i, w)
  \tag{S2}\label{eq:reachbmc2}
\end{align}
